Renal III

### 2017-05-25 renal3.rmd
added short case 1

Path

@@

-  Decline of kidney function for 3 months or more \textbf{AND}
-  Evidence of kidney damage (e.g. albuminuria or abnormal biopsy) textbf{OR}
-  GFR <60 mL/min/1.73 m2

@@

>>>>

# Readings

@@

-  Decline of kidney function for 3 months or more \textbf{AND}
-  Evidence of kidney damage (e.g. albuminuria or abnormal biopsy) \textbf{OR}
-  GFR <60 mL/min/1.73 m^2^

@@

See Dan's autoregulation of kidney [GIFT](https://drive.google.com/drive/folders/0B0QeJC_rDeMIYjZMU2VfQVR2RU0)

# Main case

**Attach the image from the whiteboard**

High anion gap is an indicator for metabolic acidosis.

Parenteral replacement is $\neg$oral (avoiding enteric system).

Hypocalcaemia $\rightarrow$ hyperPTH and hypophosphataemia + hyperphosphaturia (lack of PO4 reabsorption in the nephrons).

# Short case 1

## Trigger 1

35M presenting with increasing lethargy and weight loss. No fevers, night sweats, or pain.

Past Hx: 12 years old Dx with T1D.

Pathophysiology of diabetic nephropathy: glycosylation of basement membrane => leaky => proteins flow out => thickening of arteriole (mainly efferent) [vasoconstriction] => decreases blood flow to peritubular capillaries => they start dying.

-  ACEi dilate efferent which renoprotects against this efferent constriction at the cost of decreased GFR
-  Scarring due to HTN, glomerulopathy usually leads to atrophy due to fibrosis and it shrivels up, whereas due to diabetes has normal sized kidneys: sugar gets deposited in the kidney with sugar crystals and glycosylation (shit kidneys, low GFR, normal sized)

Presentation for CKD does not have obvious symptoms.

## Trigger 2

Antimicrobials

-  Co-trimoxazole = trimethoprim + sulphamexazole (folic acid inhibitors at different parts in the pathway; synergistic). General prophylaxis against bacteria. Good against gram(+) such as Staph.
-  Valganciclovir = antiviral. Targeting CMV
-  Amphotericin lozenges = antifungal

HLA-DR3,4 is *extremely* common with T1D.

Mechanisms of rejection

1.  HLA incompatibility
2.  ABO: blood type
3.  Rh: rhesus factor
4.  Cross-matching: check if recipient has any miscellaneous antibodies (anti-{Kell, Duffy, White} are some common ones)
